Fiber Collision Correction Method for BOSS Power Spectrum

### 2015-03-24 fc_paper/fc_paper.tex
writing intro

\begin{abstract}
With their ability to collect large amounts of redshift data, fiber-fed multi-object spectroscopic surveys dominate cosmological studies. However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the fiber-collision angular scale. These fiber-collisions ultimately leads to systematic effects on galaxy clustering measurements. Using simulated mock catalogues already extensively used in interpreting large-scale structure clustering measurements of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the power spectrum in particular. We compare current fiber-collision correction methods in the literature and assess their success in reconstructing the true power spectrum for the mock catalogues. We then present our fiber-collision correction method. Our method uses the distribution of the line-of-sight displacements between resolved fiber-collided pairs in order to statistically reconstruct clustering on small scales along with a proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$. Finally, comparison to other fiber-collision correction methods reveal that the method better reproduces the true power spectrum especially at small scales, with the added advantage that the method can be validated and calibrated in actual data. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
Through the tens of million redshifts obtained through redshift surveys, cosmological measurements are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. Most of these cosmology focused redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; CITE CITE) and the Baryon Oscillation Spectroscopic Survey (BOSS; CITECITE) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs. For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fibers even with efficient targeting strategies (e.g. \citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from each other on the sky, two separate fibers cannot be placed adjacently to separately extract the spectroscopic information. In these cases, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured. Furthermore, as we probe to higher redshifts in our cosmological studies, the fiber-collision angular scale correspond to a larger comoving scale thereby affecting our measurements on larger scales.

Though this only accounts for a small fraction of the redshifts ($< 5\%$ of the BOSS redshift survey) its effect on clustering measurements such as the power spectrum is significant and must be understood as our cosmological measurements become more detailed and sophisticated.

Fiber-collision corrections such as that proposed by \cite{Guo:2012aa} have been applied to correct for the two point correlation function. Guo et al. (2012) estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey. Unfortunately, this method cannot be easily extended for the fourier counter parts to the two-point and three-point correlation functions due to the complex geometry of the overlapping regions. Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the powerspectrum/bispectrum estimator.

In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
% Include cosmology assumption and out line of paper
\begin{itemize}
\item Even advancements in fiber positioners won't eliminate the fiber-collision issues in high density regions \cite{Morales:2012aa}. 
\item Fibercollision gets worse in comoving scales 
\item \cite{Zehavi:2002aa} FC in SDSS (example of the upweighting method) only works for fiber-collision scales and fails below it
\item Perhaps the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Makarem:2014aa}) will render fiber-collisions obsolete, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Yoon:2008aa, Guo:2012aa} LIST MORE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

@@

\section{Summary and Discussion} 
Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering statistics, in particular the power spectrum. Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k \sim 0.1 \;h/\mathrm{Mpc}$. At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum. Consequently, at these small scales the uncertainties for power spectrum measurements are dominated by systematic effects from fiber-collisions.

>>>>

\begin{abstract}
With their ability to collect large amounts of redshift data, fiber-fed multi-object spectroscopic surveys dominate cosmological studies. However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the angular fiber-collision scale. These fiber-collisions ultimately leads to systematic effects on galaxy clustering measurements. Using simulated mock catalogues already extensively used in interpreting large-scale structure clustering measurements of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the power spectrum in particular. We compare current fiber-collision correction methods in the literature and assess their success in reconstructing the true power spectrum for the mock catalogues. We then present our fiber-collision correction method. Our method uses the distribution of the line-of-sight displacements between resolved fiber-collided pairs in order to statistically reconstruct clustering on small scales along with a proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$. Finally, comparison to other fiber-collision correction methods reveal that the method better reproduces the true power spectrum especially at small scales, with the added advantage that the method can be validated and calibrated in actual data. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
Through the tens of millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) mostly use fiber fed spectrographs.

For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fibers even with efficient targeting strategies (e.g. \citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from each other on the sky, two separate fibers cannot be placed adjacently to separately extract the spectroscopic information. In these cases, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured.

Furthermore, as we probe to higher redshifts in our cosmological studies, the fiber-collision angular scale correspond to a larger comoving scale thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$, which corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the redshift bin, and fiber-collided galaxies account for $< 5\%$ of the galaxy sample. Although fiber-collided galaxies account for a relatively small fraction of the redshifts its effect on clustering measurements such as the power spectrum is significant and must be understood as clustering measurements probe to smaller scales and as we explore higher order statistics such as the three-point correlation function or the bispectrum. Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete. However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.

% Talk about the upweighting scheme and cite the different works that currently use the nearest neighbor upweighting method. 
To correct for the systematic effects of fiber collisions, a common method used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor. This method has been

\begin{itemize}
\item A paragraph that list fiber collision corrections listed in \cite{Guo:2012aa} \cite{Zehavi:2002aa}. List all clusteirng statistics measurement that uses this.
\item talk about shot-noise correction term adjustments
\end{itemize}

Recently \cite{Guo:2012aa} proposed a fiber-collision correction method for the two-point correlation function (2PCF) of the BOSS galaxies that is able to SOME PRECISION. \cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions. Unfortunately, this method cannot be applied to the Fourier counter part of the 2PCF due to the complex geometry of the overlapping regions. Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator.

In Section \ref{sec:catalog}, we present a brief description of the fiber-collided simulated mock catalogues that we use to quantify the systematic effect of fiber-collisions and to test and compare correction methods throughout the paper. After discussing the two components of our correction method in Section \ref{sec:fc_corr}, we present it in Section \ref{sec:apply}. We also test our correction method on the mock catalogues and compare it to other correction methods in Section \ref{sec:apply}. Finally in Section \ref{sec:summary} we summarize and discuss our results. 
% Include cosmology assumption and out line of paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Yoon:2008aa, Guo:2012aa} LIST MORE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

@@

\section{Summary and Discussion} \label{sec:summary}
Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering statistics, in particular the power spectrum. Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k \sim 0.1 \;h/\mathrm{Mpc}$. At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum. Consequently, at these small scales the uncertainties for power spectrum measurements are dominated by systematic effects from fiber-collisions.
